OptiFit: a fast method for fitting amplicon sequences to existing OTUs

### 2021-05-16 paper/paper.Rmd
Updates from Wednesday writing group
Added transition statements for split datasets section.

**Then we wanted to know; what fraction of sequences should be in the reference?**
To test the best reference size, reference sizes from 10% to 80% of the
sequences were created, with the remaining sequences used for the query.
OTU quality was remarkably stable across reference fraction sizes.
For example, splitting the human dataset 100 times yielded a coefficient of
variation of `r cv_fit_split_mcc_human` for the MCC score across all fractions. **TODO: revisit how to report this**

**Finally, we wanted to know the best way to select the reference sequences.**
**TODO: pick a fraction (e.g. 50%). this part is less important. figure would be supplemental.**
We also tested three methods for selecting the fraction of sequences to be used
as the reference; a simple random sample, weighting sequences by relative
abundance, and weighting by similarity to other sequences in the dataset.
OTU quality was similar with the simple and abundance-weighted sampling (median
MCCs `r mcc_fit_split_simple` and `r mcc_fit_split_abun` respectively), but
worse for similarity-weighted sampling with a median MCC of `r mcc_fit_split_dist`.
In closed reference mode, the fraction of query sequences that can be fit to the
reference OTUs increases as the reference fraction increases; from 
`r frac_fit_split_0.1`% of query sequences fit when using 10% of the dataset as 
the reference, to `r frac_fit_split_0.8`% of query sequences fit when using 80% 
of the dataset as the reference.

>>>>

While we initially tested this strategy using an even split of the data into
reference and query fractions, we then wanted to investigate whether there was
an optimal reference fraction size.
To test the best reference size, reference sizes from 10% to 80% of the
sequences were created, with the remaining sequences used for the query.
OTU quality was remarkably stable across reference fraction sizes.
For example, splitting the human dataset 100 times yielded a coefficient of
variation of `r cv_fit_split_mcc_human` for the MCC score across all fractions. **TODO: revisit how to report this**
**TODO: runtime & fraction mapped across sizes.**

**TODO: pick a fraction (e.g. 50%). this part is less important. figure would be supplemental.**
After testing the split strategy using a simple random sample to select the reference sequences, we then investigated other methods of splitting the data.
We tested three methods for selecting the fraction of sequences to be used
as the reference; a simple random sample, weighting sequences by relative
abundance, and weighting by similarity to other sequences in the dataset.
OTU quality was similar with the simple and abundance-weighted sampling (median
MCCs `r mcc_fit_split_simple` and `r mcc_fit_split_abun` respectively), but
worse for similarity-weighted sampling with a median MCC of `r mcc_fit_split_dist`.
In closed reference mode, the fraction of query sequences that can be fit to the
reference OTUs increases as the reference fraction increases; from 
`r frac_fit_split_0.1`% of query sequences fit when using 10% of the dataset as 
the reference, to `r frac_fit_split_0.8`% of query sequences fit when using 80% 
of the dataset as the reference. **TODO: report up to 90% fraction**
